### 2022-01-19 documentos/pce.tex
quito comentario de carlos

\section{PCE Maps} 
To introduce the family of Pauli component erasing maps we start with 
review basic concepts of quantum channels that will allow us to introduce some 
notation. 
% In this section we introduce the definition of Pauli component erasing maps,
% but first we go through several standard definitions needed to discuss them.
\subsection{Quantum channels} % {{{
\cpnote{Cambios importantes, qeu David revise}

Quantum channels are the most general linear operations that a quantum
system undergo independently of its past~\cite{zimansbook,cirac}.
The physical system under study will be associated with a Hilbert space
denoted by \hilbert{}, and the set of linear operators over such space will 
be denoted by $\mcB(\hilbert)$. That way, a density matrix $\rho$ of such system
 is an element of $\mcB(\hilbert)$.

>>>>

\section{PCE Maps} 
To introduce the family of Pauli component erasing maps we start with 
review basic concepts of quantum channels that will allow us to introduce some 
notation. 
% In this section we introduce the definition of Pauli component erasing maps,
% but first we go through several standard definitions needed to discuss them.
\subsection{Quantum channels} % {{{
Quantum channels are the most general linear operations that a quantum
system undergo independently of its past~\cite{zimansbook,cirac}.
The physical system under study will be associated with a Hilbert space
denoted by \hilbert{}, and the set of linear operators over such space will 
be denoted by $\mcB(\hilbert)$. That way, a density matrix $\rho$ of such system
 is an element of $\mcB(\hilbert)$.
